Near Optimal Behavior via Approximate State Abstraction

### 2016-05-21 paper/example_domains.tex
Fixed figure 6 to be figure 1 by moving label to after caption

% Subsection: Minefield.
%\subsection{Minefield}
Minefield is a test problem we are introducing that uses the Grid World dynamics of \citet{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$. We depict the original Minefield and an abstract Minefield in Figure~\ref{fig:minefield-visual}.

% Minefield Compression Visuals
\begin{figure}
\centering
\subfigure[Ground Minefield]{
\includegraphics[width=0.34\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
\label{fig:minefield-visual}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $\varepsilon=0.5$}
\end{figure}

>>>>

% Subsection: Minefield.
%\subsection{Minefield}
Minefield is a test problem we are introducing that uses the Grid World dynamics of \citet{russell1995modern} with slip probability of $x$. The reward function is such that moving up in the top row of the grid receives $1.0$ reward; all other transitions receive $0.2$ reward, except for transitions to a random set of $\kappa$ states (which may include the top row) that receive $0$ reward. (These are the states with ``mines'' in them.) We set $N=10, M=4, \varepsilon=0.5, \kappa = 5, x = 0.01$. We depict the original Minefield and an abstract Minefield in Figure \ref{fig:minefield-vis}.

% Minefield Compression Visuals
\begin{figure}
\centering
\subfigure[Ground Minefield]{
\includegraphics[width=0.34\columnwidth]{figures/ground_minefield.png}}
\subfigure[Abstract Minefield]{
\includegraphics[width=0.34\columnwidth]{figures/abs_minefield.png}}
\caption{Comparison of ground Minefield \ac{MDP} and abstract \ac{MDP}, under a $\epQ$ abstraction with $
\varepsilon=0.5$}
\label{fig:minefield-vis}
\end{figure}
